### 2016-08-18 rebuttal.tex

\question The sets support listing is unnaturally split in two by the ``This includes\ldots'' sentence which would fit better in parentheses.
\begin{solution}
This suggestion was implemented.
\end{solution}

\question Line 355, add a sentence explaining that in SymPy \texttt{str == repr}, because in Python \texttt{repr} is used to get an unambiguous valid Python code representation, while the return value of \texttt{str} is meant to be human-readable.
\begin{solution}

\end{solution}

\question Lines 359 and 379: what is 2D text representation? It seems that ``2D'' shouldn't be here.
\begin{solution}
This sentence was replaced with:
\begin{quote}
Two-dimensional (2D) textual representation of the expression can
be printed with monospace fonts via \verb|pprint|.
\end{quote}
We use here same terminology as in the Mathematica
online documentation, e.g. OutputForm function.
\end{solution}

### 2016-08-18 rebuttal.tex

\question The title ``Features'' in line 276 is ambiguous, as a ``feature''
has no precise meaning in Python (or even software libraries in general). It
should be replaced by ``Packages and modules'' or a similar more precise
wording. The same goes for ``feature'' in most other places in the paper (for
example, the caption of Table 1.\ and line 495). It would be very useful to also include actual names of the packages/modules in Table 1., as well as in any section covering those packages/modules.
\begin{solution}

\end{solution}

\question The sets support listing is unnaturally split in two by the ``This includes\ldots'' sentence which would fit better in parentheses.
\begin{solution}
This suggestion was implemented.
\end{solution}

\question Line 355, add a sentence explaining that in SymPy \texttt{str == repr}, because in Python \texttt{repr} is used to get an unambiguous valid Python code representation, while the return value of \texttt{str} is meant to be human-readable.
\begin{solution}
This footnote was added:
\begin{quote}
In SymPy, \texttt{str(expr) == repr(expr)}.  In other words,
string representation of an expression designed to be both compact,
human-readable and a valid Python code, that could be used to
recreate one.  As it was noted before, use \texttt{srepr} function to
see the exact form of an expression.
\end{quote}
\end{solution}

### 2016-08-18 printers.tex
Address question 21 of the reviewer 3

SymPy has a rich collection of expression printers.
By default, an interactive Python session will render the
\verb|str| form of an expression, which has been used in all the examples in
this paper so far. The \verb|str| form of an expression is valid Python and
roughly matches what a user would type to enter the expression.

>>>>

SymPy has a rich collection of expression printers.
By default, an interactive Python session will render the
\verb|str| form of an expression, which has been used in all the examples in
this paper so far. The \verb|str| form of an expression is valid
Python\footnote{In SymPy, \texttt{str(expr) == repr(expr)}.  In other words,
string representation of an expression designed to be both compact,
human-readable and a valid Python code, that could be used to
recreate one.  As it was noted before, use \texttt{srepr} function to
see the exact form of an expression.} and
roughly matches what a user would type to enter the expression.
